---
title: "Suburban Report - Q4 2019 "
output: 
  flexdashboard::flex_dashboard:
    storyboard: true
    social: menu
    source: embed
    theme: bootstrap
    logo: C:/Users/reinaldo.viccini/Documents/jlllogoflex.png
    
    #bootstrap
    #flatly
    #paper , dont like
    #simplex 
    #yeti , not for this
    #cerulean , not for this
    #journal, dont like
    #readable, dont like
    #spacelab , dont like
    #cosmo , default
    #lumen
    #sandstone , green dont like
    #united , purple dont like
---

```{r setup, include=FALSE}
library("flexdashboard")
library("pdftools")
library("tidyverse")
library("ggplot2")
library("ggthemes")
library("gridExtra")
library("dplyr")
library("RColorBrewer")
library("plotly")
library("dygraphs")
library("Quandl")
library("kableExtra")
library("cansim") #Stats Canada API! Great!

# Reading Historical Data from JLL

Histdata<-read.csv("C:/Users/reinaldo.viccini/Desktop/Desktop Folder/Historical Data of Office Research/CSV Version/Historical Data Vacancies 20193.csv",header = TRUE,sep=",")

#Fixing up dates so I can use Time Series., the format part is the most important
Histdata$Quarter<- as.character(Histdata$Date)
Histdata$Quarter<-as.Date(paste("01-", Histdata$Quarter, sep = ""), format = "%d-%y-%b")

#Period of Interest, this is what I change (Be careful with the format part it changes everytime I open the csv)
Period<-"2019-09-01"

#Ordering submarket by Area
Histdata$Submarket <- factor(Histdata$Submarket, levels = rev(c("Downtown","West Core", "Central Core","East Core","Suburbs","Beltline","North","Northwest","Northeast","South" ,"Greater Calgary" )))

#################################################################################################
# JLL National DAta Comparing Calgary with other cities
Histdatanational<-read.csv("C:/Users/reinaldo.viccini/Desktop/Desktop Folder/Historical Data of Office Research/CSV Version/HistNationalVac.csv",header = TRUE,sep=",")
str(Histdatanational)

#Fixing dates
Histdatanational$date2<- as.character(Histdatanational$Date)
Histdatanational$date2<- paste("01-", Histdatanational$date2, sep = "")
Histdatanational$date2<-as.Date(Histdatanational$date2, format = "%d-%y-%b")

#Delete non-Important Variables
Histdatanational<-Histdatanational[,-c(1,2,3)]
Calgary<-Histdatanational[,c(20)]

#TRansformed into a TS object, When Frequency is 4 it becomes a quarter.
Calgary<-ts(Calgary,frequency=4, start=c(2010),end=c(2019))

#Quandl Data for House Starts in Calgary, Interest rates ,etc
Quandl.api_key("YBgVd_yw_nVEY_x2fzQw")
Housestarts<- Quandl("CMHC/HSDAA_AB", start_date="2001-12-31", end_date="2019-12-31")
Housestarts$Date<- as.character(Housestarts$Date)
Housestarts$Date<-as.Date(paste(Housestarts$Date, format = "%Y-%m-%d"))

Shorttermbonds<- Quandl("BOC/V39059", start_date="2001-12-31", end_date="2019-12-31")
Shorttermbonds$Date<- as.character(Shorttermbonds$Date)
Shorttermbonds$Date<-as.Date(paste(Shorttermbonds$Date, format = "%Y-%m-%d"))

ExchangerateUSDCAD<- Quandl("FED/RXI_N_B_CA", start_date="2001-12-31", end_date="2019-12-31")
ExchangerateUSDCAD$Date<- as.character(ExchangerateUSDCAD$Date)
ExchangerateUSDCAD$Date<-as.Date(paste(ExchangerateUSDCAD$Date, format = "%Y-%m-%d"))
ExchangerateUSDCAD$Value<-1/ExchangerateUSDCAD$Value

oil<- Quandl("EIA/PET_RWTC_D", start_date="2001-12-31", end_date="2019-12-31")
oil$Date<- as.character(oil$Date)
oil$Date<-as.Date(paste(oil$Date, format = "%Y-%m-%d"))


#############################################################
#Stats Canada Data, takes ages to load so only do this once.
#get_cansim_table_overview("14-10-0287-03")
#Unemployed<-get_cansim("14-10-0287-03") %>% normalize_cansim_values
#Unemployed$GEO<-as.factor(Unemployed$GEO)
#Unemployed$Sex<-as.factor(Unemployed$Sex)
#Unemployed$Statistics<-as.factor(Unemployed$Statistics)
#colnames(Unemployed)[4] <- "Interest"
#Unemployed$Interest<-as.factor(Unemployed$Interest)
#colnames(Unemployed)[8] <- "Type"
#Unemployed$Type<-as.factor(Unemployed$Type)
#colnames(Unemployed)[6] <- "Age"
#Unemployed$Age<-as.factor(Unemployed$Age)
#Unemployed2<-subset(Unemployed , GEO=="Alberta" & Interest=="Unemployment rate" & Type=="Seasonally adjusted" & Statistics=="Estimate")


UnemploymentAlberta<-get_cansim_vector(c("Unemployment Rate"="v21581519"),
                  start_time = "2000-01-01",
                  end_time="2020-01-01")
UnemploymentAlberta$REF_DATE<-as.Date(UnemploymentAlberta$REF_DATE,format="%Y-%m-%d")



#GDP<-get_cansim("36-10-0402-01")


GDPAlberta<-get_cansim_vector(c("GDP"="v62462994"),
                  start_time = "1997-01-01",
                  end_time="2018-01-01")
GDPAlberta$REF_DATE<-as.Date(GDPAlberta$REF_DATE,format="%Y-%m-%d")

```

Q4 {.storyboard}
=========================================

### Net absorption numbers in per neighborhood in the suburbs saw the best


```{r}
Calgary<-subset(Histdata,Class=="Totals" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North"& Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period)
Calgary$Sign<-as.factor(ifelse(Calgary$Total.net.absorption..s.f..>0,"Positive","Negative"))


p<-ggplot(data = Calgary, aes(x=Submarket,y = Total.net.absorption..s.f../1000, fill= Sign,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Net Absorption S.F. : ",formatC(Calgary$Total.net.absorption..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "% of Inventory :",round((Calgary$Total.net.absorption..s.f../Calgary$Inventory..s.f..)*100,2),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab(" ")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#E30613", "#000000","grey"))+theme(legend.title = element_blank())+ theme(legend.position = "none") + scale_y_continuous(limits=c(-250, 350))
  

ggplotly(p, tooltip = "text")

```

***

- Suburban Calgary Vacancies are at their lowest level since 2017

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic


### Vacancy rates in suburban Calgary continue trending downwards and currently stand at their lowest levels since 2016

```{r}
Calgary<-subset(Histdata,Class=="Totals" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North" & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core")


p<-ggplot(data = Calgary, aes(x = Quarter, y = Total.vacancy....*100, group = Submarket,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Vacancy Rate: ",Calgary$Total.vacancy....*100,"\n",
                          "Class : ",Calgary$Class,"\n",
                          "Submarket : ",Calgary$Submarket,"\n",
                          sep="")))+
  geom_line(aes(linetype = Submarket, color = Submarket))+
  theme_classic()+ xlab("Quarter")+ ylab("Vacancy Rate (%)")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Vacancy rates(%) for Class A Buildings in the Calgary")+
  theme(legend.title=element_blank())+
  scale_linetype_manual(values=c("solid", "solid","solid","solid","solid","solid","solid"))+
  scale_size_manual(values=c(7, 2,2,1,1,1,1))+ scale_y_continuous(limits=c(0, 40))+ scale_color_brewer(palette="Dark2")

p1<-ggplotly(p, tooltip = "text")


p1$x$data[[1]]$name<-"South"
p1$x$data[[2]]$name<-"Northeast"
p1$x$data[[3]]$name<-"Northwest"
p1$x$data[[4]]$name<-"Beltline"


p1


```

***

- Suburban Calgary Vacancies are at their lowest level since 2017

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic


### Gross Rents 

```{r}

Calgary<-subset(Histdata,Class=="Totals" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North"  & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" )



p<-ggplot(data = Calgary, aes(x = Quarter, y = Average.direct.asking.gross.rent....p.s.f.., group = Submarket,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Average Asking Rents CAD : ",Calgary$Average.direct.asking.gross.rent....p.s.f..,"\n",
                          "Class : ",Calgary$Class,"\n",
                          "Submarket : ",Calgary$Submarket,"\n",
                          sep="")))+
  geom_line(aes(linetype = Submarket, color = Submarket))+
  theme_classic()+ xlab("Quarter")+ ylab("CAD per S.F.")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Gross Rents for All Buildings in the Calgary")+
  theme(legend.title=element_blank())+
  scale_linetype_manual(values=c("solid", "solid","solid","solid","solid","solid","solid"))+
  scale_size_manual(values=c(7, 2,2,1,1,1,1))+ scale_y_continuous(limits=c(20, 55))+ scale_color_brewer(palette="Dark2")

p1<-ggplotly(p, tooltip = "text")


p1$x$data[[1]]$name<-"South"
p1$x$data[[2]]$name<-"Northeast"
p1$x$data[[3]]$name<-"Northwest"
p1$x$data[[4]]$name<-"Beltline"


p1

```

***

- Me

### Vacancies by submarket

```{r}

Calgary<-subset(Histdata,Class!="Totals" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North" & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period )

p<-ggplot(data = Calgary, aes(x=Submarket,y = Total.vacancy..s.f../1000, fill= Class,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Vacant S.F. : ",formatC(Calgary$Total.vacancy..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab("submarket")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#08306b", "#6baed6","#c6dbef"))+ theme(legend.title = element_blank())+ scale_y_continuous(limits=c(0, 6000))

ggplotly(p, tooltip = "text")

```


***

```{r}
Calgary<-Calgary[,c(3,4,7)]
colnames(Calgary)[colnames(Calgary) == "Inventory..s.f.."] <- "Inventory"
kable(Calgary) %>%
  kable_styling(bootstrap_options = "striped", full_width = F, position = "left")

```







YTD {.storyboard}
=========================================


### YTD Net Absorption by Neighborhood

```{r}
Calgary<-subset(Histdata,Class=="Totals" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North" & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period )
Calgary$Sign<-as.factor(ifelse(Calgary$YTD.total.net.absorption..s.f..>0,"Positive","Negative"))


p<-ggplot(data = Calgary, aes(x=Submarket,y = YTD.total.net.absorption..s.f../1000, fill= Sign,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Net Absorption S.F. : ",formatC(Calgary$YTD.total.net.absorption..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "% of Inventory :",round((Calgary$Total.net.absorption..s.f../Calgary$Inventory..s.f..)*100,2),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab(" ")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#E30613", "#000000","grey"))+ theme(legend.title = element_blank())+ theme(legend.position = "none")+ scale_y_continuous(limits=c(-250, 350))
  



ggplotly(p, tooltip = "text")

```


***

- Me

### YTD Net Absorption by Neighborhood for Class A Assets

```{r}
Calgary<-subset(Histdata,Class=="A" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North"  & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period )
Calgary$Sign<-as.factor(ifelse(Calgary$YTD.total.net.absorption..s.f..>0,"Positive","Negative"))


p<-ggplot(data = Calgary, aes(x=Submarket,y = YTD.total.net.absorption..s.f../1000, fill= Sign,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Net Absorption S.F. : ",formatC(Calgary$YTD.total.net.absorption..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "% of Inventory :",round((Calgary$Total.net.absorption..s.f../Calgary$Inventory..s.f..)*100,2),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab(" ")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#E30613", "#000000","grey"))+ theme(legend.title = element_blank())+ theme(legend.position = "none")+ scale_y_continuous(limits=c(-250, 350))
  



ggplotly(p, tooltip = "text")

```


***

- Me


### YTD Net Absorption by Neighborhood for Class B Assets

```{r}
Calgary<-subset(Histdata,Class=="B" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North"  & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period  )
Calgary$Sign<-as.factor(ifelse(Calgary$YTD.total.net.absorption..s.f..>0,"Positive","Negative"))


p<-ggplot(data = Calgary, aes(x=Submarket,y = YTD.total.net.absorption..s.f../1000, fill= Sign,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Net Absorption S.F. : ",formatC(Calgary$YTD.total.net.absorption..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "% of Inventory :",round((Calgary$Total.net.absorption..s.f../Calgary$Inventory..s.f..)*100,2),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab(" ")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#E30613", "#000000","grey"))+ theme(legend.title = element_blank())+ theme(legend.position = "none")+ scale_y_continuous(limits=c(-250, 350))



  

ggplotly(p, tooltip = "text")

```

***

- Me


### YTD Net Absorption by Neighborhood for Class C Assets

```{r}
Calgary<-subset(Histdata,Class=="C" & Submarket!="Greater Calgary" & Submarket!="Downtown" & Submarket!="Suburbs" & Submarket!="North" & Submarket!="West Core" & Submarket!="Central Core" & Submarket!="East Core" & Quarter==Period )
Calgary$Sign<-as.factor(ifelse(Calgary$YTD.total.net.absorption..s.f..>0,"Positive","Negative"))


p<-ggplot(data = Calgary, aes(x=Submarket,y = YTD.total.net.absorption..s.f../1000, fill= Sign,
             text = paste("Date: ",Calgary$Quarter,"\n",
                          "Total Net Absorption S.F. : ",formatC(Calgary$YTD.total.net.absorption..s.f.., format="f", big.mark=",", digits=0),"\n",
                          "% of Inventory :",round((Calgary$Total.net.absorption..s.f../Calgary$Inventory..s.f..)*100,2),"\n",
                          "Class : ",Calgary$Class,"\n",
                          sep="")))+
  geom_bar(stat="identity")+coord_flip()+
  theme_classic()+
  xlab(" ")+ ylab("Square Feet (000')")+
    theme(legend.position="bottom")+ scale_fill_manual(values=c("#E30613", "#000000","grey"))+ theme(legend.title = element_blank())+ theme(legend.position = "none")+ scale_y_continuous(limits=c(-250, 350))
  




ggplotly(p, tooltip = "text")

```

***

- Me




Outlook {.storyboard}
=========================================

### New Projects in the city include the Poplar Centre, 19 royal Vista and the New University District

```{r}
library("leaflet")
leaflet() %>%
  addTiles() %>%
  addMarkers(lng=-114.028252, lat=51.152667, popup="Hexagon Campus: 11063 14th Street NE")%>%
  addMarkers(lng=-113.968759, lat=50.868499, popup="35 Cranford Way  SE")%>%
  addMarkers(lng=-114.115751, lat=51.0673455, popup="The Hub: 2416 16 Avenue NW  SE")%>%
  addMarkers(lng=-114.095144, lat=51.027065, popup="Spider Site: 3001 14th Street SW")%>%
  addMarkers(lng=-114.000887, lat=51.096372, popup="The District at North Deerfoot: 2600-2650 48th Ave NE")%>%
  addMarkers(lng=-114.069150, lat=51.005153, popup="Poplar Centre: 5512 Macleod Trail SE")%>%
  addMarkers(lng=-113.977985, lat=51.109937, popup="Westwinds Business Campus Phase III: 3687 63rd Ave NE")%>%
  addMarkers(lng=-114.148965, lat=51.079205, popup="University District: 23 East & West University Avenue NW")%>%
  addMarkers(lng=-114.055855, lat=51.044021, popup="The Platform East Village")%>%
  addMarkers(lng=-114.055855, lat=51.044021, popup="Shepard Station")


```

***

- Only 2 new projects to be delivered

- Compose maps using arbitrary combinations of map tiles, markers, polygons, lines, popups, and GeoJSON.

- Create maps right from the R console or RStudio

- Embed maps in knitr/R Markdown documents and Shiny apps

- Easily render Spatial objects from the sp package, or data frames with latitude/longitude columns

- Use map bounds and mouse events to drive Shiny logic

### Housing Starts in Alberta

```{r}
p<-ggplot(data = Housestarts, aes(x = Date, y = Total,group=1,
             text = paste("Date: ",Housestarts$Date,"\n",
                          "Total Units : ",Housestarts$Total,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("Total Number of Units.")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Gross Rents for All Buildings in the Calgary")+
  theme(legend.title=element_blank())+
  stat_smooth(method = glm, fullrange =TRUE, formula= y~poly(x,5)) +
    scale_x_date(limits = c(as.Date("2001-12-31"), as.Date("2020-12-31")))

ggplotly(p, tooltip = "text")

```

***
- Housing Starts in Calgary contintue to Decline


### Interest Rates Short Term (1-3 Year Bonds)


```{r}
p<-ggplot(data = Shorttermbonds, aes(x = Date, y = Value,group=1,
             text = paste("Date: ",Shorttermbonds$Date,"\n",
                          "Avg. Yield 1-3 Year Bonds: ",Shorttermbonds$Value,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("Interest rate (%)")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Avg Yield (%)")+
  theme(legend.title=element_blank())+
  stat_smooth(method = glm, fullrange =TRUE, formula= y~poly(x,5)) +
    scale_x_date(limits = c(as.Date("2001-12-31"), as.Date("2020-03-31")))

ggplotly(p, tooltip = "text")






```

***
- Housing Starts in Calgary contintue to Decline

### Exchange Rate USD Dollar


```{r}
p<-ggplot(data = ExchangerateUSDCAD, aes(x = Date, y = Value,group=1,
             text = paste("Date: ",ExchangerateUSDCAD$Date,"\n",
                          "CAD/USD rate: ",ExchangerateUSDCAD$Value,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("CAD/USD Spot Exchange")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Avg Yield (%)")+
  theme(legend.title=element_blank())+
  stat_smooth(method = glm, fullrange =TRUE, formula= y~poly(x,5)) +
    scale_x_date(limits = c(as.Date("2001-12-31"), as.Date("2020-02-1")))

ggplotly(p, tooltip = "text")


```

***
- Housing Starts in Calgary contintue to Decline

### Oil Prices

```{r}
p<-ggplot(data = oil, aes(x = Date, y = Value,group=1,
             text = paste("Date: ",ExchangerateUSDCAD$Date,"\n",
                          "Oil Price in USD: ",oil$Value,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("Oil Price in USD")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Avg Yield (%)")+
  theme(legend.title=element_blank())+
  stat_smooth(method = glm, fullrange =TRUE, formula= y~poly(x,5)) +
    scale_x_date(limits = c(as.Date("2001-12-31"), as.Date("2020-02-1")))

ggplotly(p, tooltip = "text")


```

***
- Housing Starts in Calgary contintue to Decline


### Unemployment Alberta


```{r}
p<-ggplot(data = UnemploymentAlberta, aes(x =REF_DATE, y = VALUE,group=1,
             text = paste("Date: ",UnemploymentAlberta$REF_DATE,"\n",
                          "Unemploment Rate Alberta: ",UnemploymentAlberta$VALUE,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("Unemployment rate (%)")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Avg Yield (%)")+
  theme(legend.title=element_blank())+
  stat_smooth(method = glm, fullrange =TRUE, formula= y~poly(x,5)) +
    scale_x_date(limits = c(as.Date("2001-12-31"), as.Date("2020-02-1")))

ggplotly(p, tooltip = "text")


```

***
- Housing Starts in Calgary contintue to Decline



### GDP Growth Alberta

```{r}
p<-ggplot(data = GDPAlberta, aes(x =REF_DATE, y = VALUE,group=1,
             text = paste("Date: ",GDPAlberta$REF_DATE,"\n",
                          "Unemploment Rate Alberta: ",GDPAlberta$VALUE,"\n",
                                                    sep="")))+
  geom_line(color = "Red")+
  theme_classic()+ xlab("Date")+ ylab("GDP Albert in (000')")+
    theme(axis.text.x=element_text(angle = -90, hjust = 0))+
  theme(legend.position="bottom")+
  ggtitle("", subtitle = "Avg Yield (%)")+
  theme(legend.title=element_blank())+
    scale_x_date(limits = c(as.Date("1997-01-01"), as.Date("2018-01-01")))

ggplotly(p, tooltip = "text")


```

### Forecast
